### 2019-01-15 manuscript.tex
Added in Financial Incentive part
All data and scripts are up to date
Intro and methods now contain information on the reward study

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be. As it was possible that participants were aware of their own ability but were not using this information, half of the participants were asked to state after having selected somewhere to stand. This was added as a potential prompt for participants to make use of this information which may have potentially improved performance \citep{chang2014self}. The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial also did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using their knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the three studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

@@

\paragraph{} The first of these factors is somewhat related to the concept of \textit{loss aversion} as described by \cite{KahnemanProspect}. Loss aversion occurs when people opt for an option that does not entail a high chance of losing. This can be seen with the option A vs. option B tasks as mentioned previously. This is argued to be evidence that losses are weighted more heavily than their equivalent gains making a small chance of success seem preferable even when this option would most likely result in a larger loss. In the context of the tasks from \cite{clarke2015failure}, it may be that participants are reluctant to commit to one target as this would ensure that should the other potential be the target for that trial, they would incur a sure loss. If the idea of loss aversion was to explain the participants suboptimal behaviours in \cite{clarke2015failure}, then this would result in participants selecting the position that gave them a more equal chance of success should either side become the target.

@@

\subsection*{Probability Matching}
\addcontentsline{toc}{subsection}{Probability Matching}
%This is just a temporary intro to this section that can be edited at any point depening on where it is positioned in the final version
\paragraph{} In many respects, the idea of spatial averaging as discussed in the context above shares many similarities to that of the issue of \textit{Probability Matching}. \textit{Probability Matching} is when people select each item based on the probability that it will appear. This is often regarded as a suboptimal behaviour as it does not offer the greatest rate of success \cite{Koehler2010}. An eaxmple of this would be if one was tasked with selecting between two options several times in a row. If option A would reward you 80\% of the time, and option B only 20\% of the time, the best course of action is to pick option A all the time as this would result in an average success rate of 80\%. Whereas trying to match the probabilities by selecting each option in proportion to its likelihood of success would only yield an average success rate of 68\%.

\paragraph{} On face value, this appears to be a misunderstanding of probability. However, if one is able to detect the likelihood of each event occurring, this information can be useful in making decisions about where to direct our efforts. In the original paradigm \citep{clarke2015failure}, each potential target was equally likely to become the actual target. One may compare this to the "\textit{Buridan's Ass}" in which a donkey is equally hungry and thirsty whilst being equidistant from a source of food and of water. With this in mind, there is no reason to opt for one target over the other as they are both equally attractive. Having two equally likely targets to aim for may have causes participants in \cite{clarke2015failure} to rely more heavily on a centre strategy than they should have given the optimal solution to the task. Committing to one side or the other may have been seen as "too risky" in such an uncertain context and so it may have appeared safer to opt for a more central location.

\paragraph{} This is what they observed; participants in the $100\%$ condition did have a higher rate of strictly matching. They suggested suggested that by giving participants the goal of aiming to be $100\%$ accurate, participants began to focus on overall accuracy rather than treating each trial as independent of the others, something they argue is more likely to result in matching behaviour \citep{Gao2015}. Thus, they argue that the tendency to engage in matching behaviour is similar to the idea of avoiding loss \citep{KahnemanProspect}. By always choosing the more likely option, it is possible to view this as accepting some sure losses.

@@

@@

\subsection*{Preface}
\addcontentsline{toc}{subsection}{Prefac}
\paragraph{} The search for patterns can cause people to perform tasks in a less than optimal way due to this being a cognitively demanding task in itself \citep{wolford2004searching}. In \textit{Experiments 1 \& 2}, there was still the possibility for participants to search for patterns to exploit which may have interrupted the use more relevant information. As such, in \textit{Experiment 3} the aim to was to remove this from the task design and thus remove any reason for participants to try and "discover" an underlying pattern in the task. To do this, instead of telling participants that one of the potential locations would become the target, they were instead to try and achieve both on every trial.

@@

>>>>

\paragraph{} This possibility was investigated in \cite{James2017} using the \textit{Throwing Task} with the added measure of what participants understood their ability to be. As it was possible that participants were aware of their own ability but were not using this information, half of the participants were asked to state after having selected somewhere to stand. This was added as a potential prompt for participants to make use of this information which may have potentially improved performance \citep{chang2014self}. The results of this experiment suggested that all participants had a very clear understanding of their own ability. Prompting participants to think about their accuracy on each trial also did not appear to make participants better able to solve the problem presented to them. The results of \cite{James2017} appear to suggest either a failing of \textit{Bounded Rationality} in that participants were not considering/using their knowledge of their ability to accuractely throw bean bags appropriately, or that they were simply more focused on other aspects of the task that may have caused them to ignore this information. In the four studies presented here, the aim was to investigate what aspects of the task may have interfered with the participants' ability to figure out the optimal strategy.

\subsection*{Probability Matching}
\addcontentsline{toc}{subsection}{Probability Matching}
%This is just a temporary intro to this section that can be edited at any point depening on where it is positioned in the final version
\paragraph{} The first of these factors to be investigated is that of \textit{Probability Matching}. \textit{Probability Matching} is when people select each item based on the probability that it will appear. This is often regarded as a suboptimal behaviour as it does not offer the greatest rate of success \citep{Koehler2010}. An eaxmple of this would be if one was tasked with selecting between two options several times in a row. If option A would reward you 80\% of the time, and option B only 20\% of the time, the best course of action is to pick option A all the time as this would result in an average success rate of 80\%. Whereas trying to match the probabilities by selecting each option in proportion to its likelihood of success would only yield an average success rate of 68\%.

\paragraph{} On face value, this appears to be a misunderstanding of probability. However, if one is able to detect the likelihood of each event occurring, this information can be useful in making decisions about where to direct our efforts. In the original paradigm \citep{clarke2015failure}, each potential target was equally likely to become the actual target. One may compare this to the "\textit{Buridan's Ass}" in which a donkey is equally hungry and thirsty whilst being equidistant from a source of food, and of water. With this in mind, there is no reason to opt for one target over the other as they are both equally attractive. Having two equally likely targets to aim for may have caused participants in \cite{clarke2015failure} to rely more heavily on a centre strategy than they should have given the optimal solution to the task. Committing to one side or the other may have been seen as "too risky" in such an uncertain context and so it may have appeared safer to opt for a more central location.

\paragraph{} This is what they observed; participants in the $100\%$ condition did have a higher rate of strictly matching. They suggested that by giving participants the goal of aiming to be $100\%$ accurate, participants began to focus on overall accuracy rather than treating each trial as independent of the others, something they argue is more likely to result in matching behaviour \citep{Gao2015}. Thus, they argue that the tendency to engage in matching behaviour is similar to the idea of avoiding loss \citep{KahnemanProspect}. By always choosing the more likely option, it is possible to view this as accepting some sure losses.

@@

\paragraph{} As discussed above, it's possible that probability matching as a strategy may emerge from an attempt to avoid being unsuccessful \citep{Gao2015}. This can be seen as related to the idea of \textit{loss aversion} as described by \cite{KahnemanProspect}. Loss aversion occurs when people opt for an option that does not entail a high chance of losing. This can be seen with the option A vs. option B tasks as mentioned previously. This is argued to be evidence that losses are weighted more heavily than their equivalent gains making a small chance of success seem preferable even when this option would most likely result in a larger loss. In the context of the tasks from \cite{clarke2015failure}, it may be that participants are reluctant to commit to one target as this would ensure that should the other potential be the target for that trial, they would incur a sure loss. If the idea of loss aversion was to explain the participants suboptimal behaviours in \cite{clarke2015failure}, then this would result in participants selecting the position that gave them a more equal chance of success should either side become the target. This idea of reducing the chance of failure on a trial can also be observed in the speeded reaching literature which may offer insight as to why participants were (in general) hesistant to fully commit to one option or the other in \cite{clarke2015failure}.

@@

@@

\subsection*{Financial Incentives}
\addcontentsline{toc}{subsection}{Financial Incentives}

\paragraph{} It is also possible that some participants lack the incentive to perform the task to the best of their ability. \cite{phillips1966conservatism} investigated this idea by tasking participants with estimating whether a bag they had been handed contained predominantly red or blue chips. They were told there were 10 bags in total with $X$ containing predominantly red chips and $10 - X$ containting predominantly blue chips. They were then told that the bags that contained mainly red chips either contained 70\% red chips and 30\% blue, or 60\% red and 40\% blue with the inverse of these being true for the predominantly blue bags. They were then presented with 20 chips from the selected bag and were asked to give an estimate of how likely the bag the chips were drawn from was a majority red or majority blue bag. What they found was that participants estimates were fairly conservative when compared to what would be expected via Bayesian inference. They questioned whether this could be due to a lack of incentive to perform this task more effortfully.

\paragraph{} They then repeated this experiment but with a payoff schedule associated with their performance in the task. What they found was that the participants that were offered an incentive to be accurate demonstrated a higher amount of learning. This meant that later in the experiment, they would offer more accurate estimates than compared to the unpaid participants. However, they still remained somewhat conservative.

\paragraph{} Another example of a payoff structure altering the behaviour of participants can be seen in \cite{Goodnow1955} in which participants that were rewarded for performance were more likely to employ a more optimal strategy. They tasked participants with making judgements of which event would occur on each trial. The likelihood of each event occuring was set in one of three ways; being equally likely, a 70\% bias in favour of one event, or a 90\% bias in favour of one event occurring. Half the participants were told that the task was one of learning and that they were to uncover some underlying principle, whereas the other half were told that the task was one of gambling in which they were to place a bet on which event was likely to occur on each trial. They found that participants in the gamble condition when there was a 70\% bias were more likely to opt for a \textit{maximising} strategy than those in the problem solving condition. This was also true for the 90\% bias condition, but the effect appeared less pronounced.

\paragraph{} Although these studies do suggest that a financial incentive may have pushed some participants to perform the task in a more optimal way, it did not cause them to perform the tasks perfectly optimally. In a review by \cite{Camerer1999}, it is argued that a financial incentive is not entirely enough to remove all irrational behaviours. This can clearly be seen in \cite{morvan2012human} in which participants receieved a small sum of money for every successful trial. Despite this financial incentive, participants did not appear to behave any differently to those in \cite{clarke2015failure} who did not pay their participants any amount for successful trials.

\paragraph{} However, it is possible that in the original setup employed by \cite{morvan2012human} that participants were still likely to seek out locations that provided them an equal chance of success, or they may have still seen the task as something of a problem to solve. As such, we feel there is still scope to introduce a financial incentive in such a way that would be able to investigate other ideas.

\paragraph{} For example, as mentioned before, participants may simply be demonstrating a loss aversion habit in choosing to stand more central to stand rather than comitting to one or the other. Similar to as discussed above, both targets were initially of the same value either in their actual potential worth \citep{morvan2012human} or in their odds of containing the target \citep{clarke2015failure} and as such this may cause participants to follow a pattern of selecting a location to give a reasonably similar chance of success for both potential targets.

@@

\subsection*{Preface}
\addcontentsline{toc}{subsection}{Preface}
\paragraph{} The search for patterns can cause people to perform tasks in a less than optimal way due to this being a cognitively demanding task in itself \citep{wolford2004searching}. In \textit{Experiments 1 \& 2}, there was still the possibility for participants to search for patterns to exploit which may have interrupted the use more relevant information. As such, in \textit{Experiment 3} the aim to was to remove this from the task design and thus remove any reason for participants to try and "discover" an underlying pattern in the task. To do this, instead of telling participants that one of the potential locations would become the target, they were instead to try and achieve both on every trial.

@@

\section*{Experiment 4: Unequal Reward}
\addcontentsline{toc}{section}{Experiment 3: Unequal Reward}

\subsection*{Preface}
\addcontentsline{toc}{subsection}{Preface}
\paragraph{} As mentioned before, in \textit{Experiment 1}, participants were tasked with tracking a fairly abstract concept of probability. They would have needed to recognise that the location with the highest likelihood of containing the target would reward them with the greatest rate of return in the long term should they have consistently selected this option. As such, it is possible that participants did not see the more likely option as being more valuable, but instead would try to make use of this information in another way. As mentioned in the introduction, \cite{Goodnow1955} demonstrated that when participants were offered a financial incentive for success, they were more likely to make use of a maximising strategy over the, in this context, less optimal alternative of probability matching. In \textit{Experiment 4}, we attempted to investigate this by intorducing a very clear, external reward for successful performance in the task.

\pararaph{} However, as discussed above in relation to the similarity of results obtained by both \cite{clarke2015failure}, who did not pay participants, and \cite{morvan2012human}, who did pay participants, both targets were not necessarilly equal in value for this experiment. In this task, participants were given 50p on each trial and were told they could choose to split the money equally across the potential targets (i.e. 25p/25p) or unequally (i.e. 40p/10p) prior to each trial. Using this setup, we are able to investigate whether participants that are more likely to opt for the unequal split would demonstrate a stronger tendency to stand closer to one hoop over the other.

\subsection*{Methods}
\addcontentsline{toc}{subsection}{Methods}
\subsubsection*{Participants}
\paragraph{} \textit{Fill this in when we get the results}

\subsubsection*{Procedure} 
\paragraph{} Participants signed a consent which contained details about the reward schedule and how much they could expect to achieve on average. All participants were given £4 as a baseline and were told that they could expect to earn an addtional amount ranging from £0 to £4.80 depending on their performance. They were also told that we expected them to earn between £1.50 and £2.50 on average.

\paragraph{} This experiment made use of the \textit{Throwing Task} and as such, followed a similar procedure to that of \textit{Experiments 2 \& 3}. However, in this experiment, both the measuring and decision phases took place in one session. First, participants were taken to the paved area in order to measure their throwing ability across several distances. After which, they were taken to perform a computer task which was simply to occupy their time whilst the experimenter set up the hoops for the second session much in the same way as before. For this computer task, participants were to detect the presence or absence of a target polygon that was presented amongst a mixture of polygons for 200ms. For the final task, participants were taken back to the paved area to perform the decision phase.

\paragraph{} There were two main changes to the paradigm for this experiment. Firstly, instead of calculation 3 points, 4 were calculated so as to avoid using the somewhat ambiguous 50\% accuracy point. Now, the points at which participants were 90\%, 75\%, 25\%, and 10\% accurate were used. Addtionally, participants were now told they had 50p to split between the two target items in one of two ways. They could either split it equally across both potential targets (25p/25p) or make it an 80/20 split (40p/10p). Participants were asked how they would like to split the money before they made a choice about where to stand. If they opted to make an unequal split, they were asked which hoop they would like to be worth 40p and which 10p. Participants were informed that the target hoop had been predetermined so that each hoop was equally likely to be the target on each trial and that there was no pattern. It was reaffirmed that any money they earned by successfully throwing the bean bag into the target hoop would be given to them upon completing the experiment. Participants would then pick a place to stand, at which point they would be told which hoop was the target for that trial and their standing position was recorded covertly.

\begin{figure}[ht!]%{L}{0.5\textwidth}
	%\vspace{-0.7cm}
	\includegraphics[scale=0.9]{Figures/Experiment_5_Unequal_Reward/prop_and_position}
	\centering
	\captionsetup{justification=centering}
	\caption{These plots show the proportion of times each participant opted for an unequal or equal split (\textit{left}) and their normalised standing position during the decision phase colour coded to show whether the trial was an unequal or equal split (\textit{right})}
	\label{fig:DecisionPhase_Reward}
\end{figure}
